\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2024-05-27 scratch/notes_john/JSS-article/JSS-article-3.Rmd
tweak JSS draft paper

mod <- train(x = attrition[, c("JobSatisfaction", "Gender",
                               "MonthlyIncome")],
             y = attrition$Attrition,
             method = glm_mod,
             trControl = trainControl(method="LOOCV"))
mod # reports complement of Bayes-rule criterion
```

>>>>

mod <- train(x = attrition[, c("JobSatisfaction", "Gender",
                               "MonthlyIncome")],
             y = attrition$Attrition,
             method = glm_mod,
             trControl = trainControl(method="LOOCV"))
mod # reports complement of Bayes-rule criterion
```
In fairness, \pkg{caret} really isn't intended for this kind of simple CV computation.

### 2024-05-27 scratch/notes_john/JSS-article/JSS-article-3.tex
tweak JSS draft paper

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 799417
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.20609
bias-adjusted cross-validation criterion = 19.19442
95% CI for bias-adjusted CV criterion = (15.73743, 22.6514)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat) {
  if (!all(y %in% c(0, 1)))
    stop("response values not all 0 or 1")
  if (any(yhat < 0) ||
      any(yhat > 1))
    stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x1118adc78>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}

@@

>>>>

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 507470
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.41715
bias-adjusted cross-validation criterion = 19.39447
95% CI for bias-adjusted CV criterion = (15.86881, 22.92014)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat) {
  if (!all(y %in% c(0, 1)))
    stop("response values not all 0 or 1")
  if (any(yhat < 0) ||
      any(yhat > 1))
    stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x14ad5f380>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}

@@

In fairness, \pkg{caret} really isn't intended for this kind of simple
CV computation.
